HFI in RISC-V

### 2025-05-01 paper.tex
added CVE info to security section

>>>>

Equally important, HFI tackles concrete flaws that consistently slip past software guards. Software-only SFI cannot stop transient-execution attacks such as Spectre (CVE-2017-5753, CVE-2017-5715): an attacker can speculatively jump over the compiler-inserted bounds checks and leak data. Because HFI performs the range comparison inside the load/store pipeline and stalls the access until the check resolves, the classic Spectre gadgets are rendered unexploitable. The same in-pipeline enforcement also neutralises newer variants (e.g., Spectre v4 and Load Value Injection) without utilizing costly lfences throughout the code base.

At the same time, HFI preserves the ability to confine more “traditional” memory-safety bugs, such as out-of-bounds errors, that SFI already blocks—while doing so with better performance. Isolating OpenSSL in an HFI sandbox still prevents the Heartbleed over-read (CVE-2014-0160) from escaping into adjacent heaps, but avoids the 25–35\% overhead that guard-page faults imposed in process-based SFI. Likewise, keeping vulnerable image decoders (e.g., the 2023 libwebp heap overflow) in an HFI region lets a browser switch into and out of the decoder in ~80 ns—about the cost of a function call—rather than launching a heavyweight renderer process. In short, HFI simultaneously closes the speculative side-channels that SFI misses and slashes the overhead of the mitigations SFI already provides.
